Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-08 paper/main.tex
composition diagrams

Here we present a very brief summary of topics, for more information Hatcher\cite{hatcherAlgebraicTopology2002}, Munkres\cite{munkresElementsAlgebraicTopology1984}, and Spanier \cite{spanier1989algebraic}.

@@

\begin{equation}
  \label{eq:artist:presheaf}
  \begin{tikzcd}[row sep=small]
    U_1 \arrow[dd, "\iota"'] & {\Gamma(U_1, \dtotal)}                              \\
    {} \arrow[r, "\sheaf_{\dtotal}"]   & {}                                                  \\
    U_2                      & {\Gamma(U_2, \dtotal)} \arrow[uu, "\iota^*"']
    \end{tikzcd}
\end{equation}

@@

\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \Gamma(\mathcal{K}, \dfiber) & \\
{} \arrow[rr, "\varphi", Rightarrow, shift right, shorten=3.5em] & & {} \\
    & \mathcal{\dbase}^{op} \arrow[uu, "\sheaf_{\dtotal}", bend left] \arrow[uu, "\sheaf_{\dtotal}"', bend right] &   
\end{tikzcd}
\end{equation}

@@

The graphic category $\mathcal{\gtotal}$ consists of the functor object $\sheaf_{\gtotal}: \mathcal{S}^{op} \rightarrow \Gamma(\mathcal{S}, \gtotal)$ and morphisms between sheaves. The category $\mathcal{S}$ is the category of open sets $\{U\}$ over the graphic base space \gbase. The set of sets of sections $\Gamma(\mathcal{S}, \gtotal)$ is a subcatagory of \texbf{Set}.

@@

\subsubsection{Shared Index}
\begin{figure}[!h]
  \centering
  \subfloat[$\dbase_c = \dbase_a \cap \dbase_b$]{\includegraphics[width=.4\columnwidth]{union_k.png}%
  \label{fig:artist:union:k}}
  %\hfill
  \subfloat[$\dbase_c = \varnothing$]{\includegraphics[width=.4\columnwidth]{disjoint_k.png}%
  \label{fig:artist:union:disjoint_k}}
  \caption{In \autoref{fig:artist:union:k}, the input object $\sheaf_{\dtotal}$ encodes a continuous function over spaces $\dtotal_a$, $\dtotal_b$ 
  and overlapping space $\dtotal_c$. In this figure, the visual transformation is to a point on the line on screen. An artist that preserves the continuity of the function must generate graphics such that functions evaluted  $\dbasepoint \in \dbase_a \cap \dbase_b$}
\end{figure}

An example of overlapping indexing is a parallelized verion of a sliding window algorithm where window overlaps must resolve to the same value at the same position \cite{chuTimeSeriesSegmentation1995};

\begin{equation}
\label{eq:artist:intersection:basespace}
\begin{tikzcd}
  \dbase_{c} \arrow[d, "\iota", hook] \arrow[r, "\iota", hook] & \dbase_{b} \arrow[d, "i_{\dbase_b}"]      \\
  \dbase_{a} \arrow[r, "i_{\dbase_a}"]                         & \dbase_{a} \bigsqcup_{\dbase_{c}}\dbase_{b}
  \end{tikzcd}
\end{equation}
where the projection functions $i_{\dbase_a},i_{\dbase_b}$ behave such that $i_{\dbase_a}(\dbasepoint)|_{\dbasepoint \in \dbase_b} = \left[\dbasepoint\right]$, $i_{\dbase_b}(\dbasepoint)|_{\dbasepoint \in \dbase_b} = \left[\dbasepoint\right]$, meaning the projection functions yield equivalent points in the disjoint union $\dbase_a \bigsqcup_{\dbase_c} \dbase_b$. Data that is completely disjoint in the index, as shown in \autoref{fig:artist:union:disjoint_k}, is a special case where $\dbase_c=\varnothing$ and therefore there is no constraint on the artist with regards to how this data is rendered.

\subsubsection{}{Shared Fields}

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{intersection_f.png}
  \caption{The fiber spaces $F_a, F_b$ have a shared fiber space $F_c$. If they are input into the same artist $A_1$, then an equivariant transformation is one where $F_c$ is transformed to a visual element in a consistent matter. In this figure, $F_c$ is mapped to the x-axis for both $F_a$ and $F_b$.}
  \label{fig:artist:compose:union_fiber}
\end{figure}
an example of expecting consistency in overlapping fields are the multiple view constraints described by Qu and Hullman \cite{hullmanKeeping2018}. 
\begin{equation}
  \label{eq:artist:intersection:fiber}
  \begin{tikzcd}
    F_a\times{_{F_c}}F_b     & F_a \arrow[d, "proj_a"] \\
    F_b \arrow[r, "proj_b"'] & F_c                    
    \end{tikzcd}
\end{equation}

% introduce notion of equivariant fiber, chasing diagram of F is different Gamma - Kosara and Zeminiskwy differentiable glyph 
% case 1: F3 \subset F1, {JFK} \in {JFK, EWR}
% case 2: F1 = F3 \times F1, F2= F3 \times F2, 
  % F1 ->F3 is projection -> Fiber consistency
% in that case, we can form the plus operator, disjoint union of A1 + A2 going in is consistent on subspace

@@

\begin{definition} Following from \label{def:artist:} the artist \vartist is a special case of  natural transformations
  \begin{equation}
    \vartist: \Gamma(\dtotal, \dbase)\nrightarrow \Gamma(\gtotal, \gbase)
  \end{equation}
  between the profunctor objects $\Gamma(E),\Gamma(H)$ that preserves continuity and equivariance.
\end{definition}
  Natural transformations are functions that map functions between categories (functors) to other functors in a structure preserving way \cite{riehlCategoryTheoryContext, spanier1989algebraic, fongInvitationAppliedCategory2019}.

@@

\begin{equation}
  \label{eq:artist:construction:all}
  \begin{tikzcd}
      \dtotal \arrow[r, "\vchannel"] \arrow[rd, "\pi"'] & \vtotal \arrow[d, "\pi"] & \vindex^*\vtotal \arrow[r, "\vmark"] \arrow[d, "\vindex^*\pi"'] \arrow[l, "\vindex^*"'] & \gtotal \arrow[ld, "\pi"] \\
                                            & \dbase                  & \gbase \arrow[l, "\vindex"']                                              &                    
      \end{tikzcd}
\end{equation}

@@

But actually multiple variables please
\begin{equation}
  \label{eq:math:artist:nu}
  \{\vchannel_{0}, \ldots, \vchannel_{n}\}: \{\dsection_{0}, \ldots, \dsection_{n}\} \mapsto \{\vsection_{0}, \ldots, \vsection_{n}\}
\end{equation}

>>>>

Here we present a very brief summary of fiber bundles, for more information see Hatcher\cite{hatcherAlgebraicTopology2002}, Munkres\cite{munkresElementsAlgebraicTopology1984}, and Spanier \cite{spanier1989algebraic}.

@@

\begin{equation}
  \label{eq:artist:presheaf}
  \begin{tikzcd}[column sep=small]
    {\Gamma(U_1, \dtotalc)}                                       & {}                                                    & {\Gamma(U_2, \dtotalc)} \arrow[ll, "\iota^*"', hook'] \\
                                                                  &                                                       &                                                       \\
    U_1 \arrow[uu, "\sheaf_{\dtotal}"] \arrow[rr, "\iota"', hook] & {} \arrow[uu, "\sheaf_{\dtotal}" description, dotted] & U_2 \arrow[uu, "\sheaf_\dtotal"']                    
    \end{tikzcd}
\end{equation}

@@

\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \mathcal{\dtotalc} & \\
{} \arrow[rr, "\dfuncc", Rightarrow, shift right, shorten=3em] & & {} \\
    & \mathcal{\dbasec}^{op} \arrow[uu, "\sheaf_{\dtotalc}", bend left] \arrow[uu, "\sheaf_{\dtotalc}"', bend right] &   
\end{tikzcd}
\end{equation}

@@

\note{rewrite paragraph}
The graphic category $\mathcal{\gtotalc}$ consists of the functor object $\sheaf_{\gtotalc}: \mathcal{\gbasec}^{op} \rightarrow \Gamma(\mathcal{\gbasec}, \gtotal)$ and morphisms between sheaves. The category $\mathcal{\gbasec}$ is the category of open sets $\{U\}$ over the graphic base space \gbase. The set of sets of sections $\Gamma(\mathcal{\gbase}, \gtotal)$ is a subcatagory of \textbf{Set}.

@@

\subsubsection{Shared Index}
\begin{figure}[!h]
  \includegraphics[width=\columnwidth]{k_union.png}
  \label{fig:artist:union:disjoint_k}}
  \caption{In \autoref{fig:artist:union:k}, the input object $\sheaf_{\dtotal}$ encodes a continuous function over spaces $\dtotal_a$, $\dtotal_b$ 
  and overlapping space $\dtotal_c$. In this figure, the visual transformation is to a point on the line on screen. An artist that preserves the continuity of the function must generate graphics such that functions evaluated  $\dbasepoint \in \dbase_a \cap \dbase_b$}
\end{figure}

An example of overlapping indexing is a parallelized version of a sliding window algorithm where window overlaps must resolve to the same value at the same position \cite{chuTimeSeriesSegmentation1995};

\begin{equation}
\label{eq:artist:intersection:basespace}
\begin{tikzcd}
  \dbasec_{c} \arrow[d, "\iota", hook] \arrow[r, "\iota", hook] & \dbasec_{b} \arrow[d, "i_{\dbasec_b}"]      \\
  \dbasec_{a} \arrow[r, "i_{\dbasec_a}"]                         & \dbasec_{a} \bigsqcup_{\dbasec_{c}}\dbasec_{b}
  \end{tikzcd}
\end{equation}

where the projection functions $i_{\dbase_a},i_{\dbase_b}$ behave such that $i_{\dbase_a}(\dbasepoint)|_{\dbasepoint \in \dbase_b} = \left[\dbasepoint\right]$, $i_{\dbase_b}(\dbasepoint)|_{\dbasepoint \in \dbase_b} = \left[\dbasepoint\right]$, meaning the projection functions yield equivalent points in the disjoint union $\dbase_a \bigsqcup_{\dbase_c} \dbase_b$. Data that is completely disjoint in the index, as shown in \autoref{fig:artist:union:disjoint_k}, is a special case where $\dbase_c=\varnothing$ and therefore there is no constraint on the artist with regards to how this data is rendered.

\subsubsection{Shared Fields}

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{intersection_f.png}
  \caption{The fiber spaces $F_a, F_b$ have a shared fiber space $F_c$. If they are input into the same artist $A_1$, then an equivariant transformation is one where $F_c$ is transformed to a visual element in a consistent matter. In this figure, $F_c$ is mapped to the x-axis for both $F_a$ and $F_b$.}
  \label{fig:artist:compose:union_fiber}
\end{figure}

\begin{equation}
  \label{eq:artist:intersection:fiber}
  \begin{tikzcd}
    \dfiberc_{a}\times \dfiberc_{b} \arrow[d, "proj_b"] \arrow[rr, "proj_a"] &  & \dfiberc_{a} \arrow[d, "proj_c"] \\
    \dfiberc_{b} \arrow[rr, "proj_b"]                                                  &  & \dfiberc_{c}                    
    \end{tikzcd}
\end{equation}

@@

\begin{definition} Following from \label{def:artist:} the artist \vartist is a special case of  natural transformations

  %% this equation is actually on sheafs and is not a map 
  \begin{equation}
    \vartist: \Gamma(\dtotal, \dbase)\nrightarrow \Gamma(\gtotal, \gbase)
  \end{equation}
  between the profunctor objects $\Gamma(E),\Gamma(H)$ that preserves continuity and equivariance.
\end{definition}
  Natural transformations are functions that map functions between categories (functors) to other functors in a structure preserving way \cite{riehlCategoryTheoryContext, spanier1989algebraic, fongInvitationAppliedCategory2019}.

@@

%%% no arrow V->H
%%% Q is defined at the level of Gamma\begin{equation}
\begin{equation}
  \label{eq:artist:construction:all}
  \begin{tikzcd}
    \dtotalc \arrow[rr, "\vchannel"] \arrow[rdd, "\pi"] &         & \dtotalc \arrow[ldd, "\pi"'] & \mathcal{\vtotalc}                                                        & Im_{\vmarkc} \subset \gtotalc                     \\
    &         &                              & {} \arrow[r, "\vmarkc"]                                                   & {}                                                \\
    & \dbasec &                              & \mathcal{\dbasec} \arrow[uu, "\sheaf_{\vtotalc}"] \arrow[r, "\vindexc^*"] & \mathcal{\gbasec} \arrow[uu, "\sheaf_{\vmarkc}"']
    \end{tikzcd}
\end{equation}

@@

\paragraph{Multiview Constraints}
\begin{figure}[!h]
  \centering
  \subfloat[No shared fields]]{\includegraphics[width=.4\columnwidth]{exploding_artist.png}%
  \label{fig:artist:union:k}}
  %\hfill
  \subfloat[Shared fields]{\includegraphics[width=.4\columnwidth]{combined_artist.png}%
  \label{fig:artist:union:disjoint_k}}
  \caption{In \autoref{fig:artist:union:k}, the input object $\sheaf_{\dtotal}$ encodes a continuous function over spaces $\dtotal_a$, $\dtotal_b$ 
  and overlapping space $\dtotal_c$. In this figure, the visual transformation is to a point on the line on screen. An artist that preserves the continuity of the function must generate graphics such that functions evaluted  $\dbasepoint \in \dbase_a \cap \dbase_b$}
\end{figure}

The concept that shared data fields should be encoded visually in a consistent is formally expressed by Qu and Hullman \cite{hullmanKeeping2018} as the notion that the same field should have the same scale.

\begin{equation}
  \label{eq:math:artist:nu}
  \{\vchannel_{0}, \ldots, \vchannel_{n}\}: \{\dsection_{0}, \ldots, \dsection_{n}\} \mapsto \{\vsection_{0}, \ldots, \vsection_{n}\}
\end{equation}
